---
title: "Cabbages"
author: "Sophia Castellon"
date: "1 October 2024"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

$H_0$: There is no difference in the average vitC between c39 and c52. 

$H_A$: There is a difference in the average vitC between c39 and c52.

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

vitC ~ cultivation method 
vitC is an interger which is numerical and cultivation is factor which makes it categorial    
using file num~cat   

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(VitC~Cult,data=veggy)
```

This box plot shows that the VitC in c52 is greater than c39. 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```

The average VitC for c39 is 51.5, and the average VitC for c52 is 64.4, meaning c52 has a larger average of VitC. 

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```

The P value is .0000000345, this is less than 0.05, so we reject the null hypothesis and conclude the c52 is better than c39 for VitC cultivation. 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

We reject null hypothesis because it is less than .05, the p-value is 0.0000000345. There is a difference in the vitC level in the two cultivations. The c52 has a higher vitC level. 
